Optimized average-based embeddings for word sense disambiguation problem

### 2019-02-11 paper/main.tex

Independently of some noise caused by the random order of training data, the optimized model is much better than the base model (10-20\% absolute improvement w.r.t. top-1 accuracy on the test set).
Improvement is most visible for longer context lengths, which achieved relatively poor results in the baseline experiment.
It seems, that a simple optimization may help alleviate the problems with ambiguous embeddings of long contexts (\ref{sec:limitations}).

@@

\begin{figure}
    \centering
    \caption{Influence of \(\alpha\) parameter value on top-1 and top-3 accuracies for \(l=3\). Blue line denotes the average result from 30 runs, dotted lines denote worst and best result. The value for \(\alpha=0\) is the result achieved by the baseline model (\ref{sec:baseline}).}
    \label{fig:exp2_alpha}
    \includegraphics[scale=0.6]{res/exp2_alpha_top_acc.png}
\end{figure}

@@

Low values of \(\beta\) seem to slightly improve the performance of our optimization method w.r.t. top-1 accuracy (~1\% absolute improvement).
High values of \(\beta\) suffer from a similar problem to high values of \(\alpha\), causing too much disruption to keyword embeddings.

>>>>

Independently of some noise caused by the random order of training data, the optimized model is much better than the base model (12-36\% relative, 10-20\% absolute improvement w.r.t. top-1 accuracy on the test set).
Improvement is most visible for longer context lengths, which achieved relatively poor results in the baseline experiment.
It seems, that a simple optimization may help alleviate the problems with ambiguous embeddings of long contexts (\ref{sec:limitations}).

@@

\begin{figure}[H]
    \centering
    \caption{Influence of \(\alpha\) parameter value on top-1 and top-3 accuracies for \(l=3\). Blue line denotes the average result from 30 runs, dotted lines denote worst and best result. The value for \(\alpha=0\) is the result achieved by the baseline model (\ref{sec:baseline}).}
    \label{fig:exp2_alpha}
    \includegraphics[scale=0.6]{res/exp2_alpha_top_acc.png}
\end{figure}

@@

Low values of \(\beta\) seem to slightly improve the performance of our optimization method w.r.t. top-1 accuracy (about 1\% absolute and relative improvement).
High values of \(\beta\) suffer from a similar problem to high values of \(\alpha\), causing too much disruption to keyword embeddings.
